Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-30 draft/ms_v5.tex
Minor changes

    Fig \ref{fig:cmodel_mag} shows the precision and accuracy of \cmodel{} magnitude 
    in each band using the same format as Fig \ref{fig:psf_mag}.

@@

    The typical precision of $i$-band flux using \forced{} \cmodel{} is at 
    ${\sim}7-9$\% level in the \texttt{goodSeeing} \tract{} at 
    $i_{\mathrm{Input}}<24.0$ mag. 
    It moderately degrades to ${\sim}11$\% at $25.0$ mag. 
    The performance is similar in $i$ band for the \texttt{badSeeing} \tract{}. 
    At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the accuracies of \forced{} \cmodel{}
    magnitudes change from \plus{}$0.041$ mag to \minus{}$0.006$ mag, which suggest
    that \forced{} \cmodel{} photometry is unbiased down to the very faint end.

@@

    The precision of \forced{} \cmodel{} photometry is consistent across all filters.
    For the $g$, $r$, and $z$ bands, the statistical uncertainties are very similar to
    $i$-band results between $20.0$ and $25.0$ mag.
    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
    across the entire input magnitude range.
    The precision for the $y$ band is slightly worse, ranging from 9\% to 17\% in the
    same magnitude bins.
    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
    the $y$ band at $>24.0$ mag. 
    This bias in the $y$ band flux is equal to \minus{}0.07 at $24.0$ mag to 
    \minus{}0.22 mag at 25.0 mag. 
    Worse seeing conditions and a higher background noise level mean that it is more
    difficult to detect faint objects in the $y$ band.
    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
    around the detection threshold.

@@

    Fig \ref{fig:cmodel_color} evaluates the precision and accuracy of \forced{} 
    $(g-i)$ and $(i-y)$ \cmodel{} colors using the same format as 
    Fig \ref{fig:psf_color}. 
    We find that \hscpipe{} provides reliable \cmodel{} colors for synthetic 
    galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
    For $(g-i)$ colors, the statistical uncertainty at $i_{\mathrm{Input}}{\sim}21.0$ 
    mag is ${\sim}0.04$ mag.
    The statistical uncertainty increases to ${\sim}0.11$ mag at 
    $i_{\mathrm{Input}}{\sim}25.0$ mag.
    The $(i-y)$ colors show similar results.

    The performance of \forced{} \cmodel{} color does not depend on seeing and is 
    unbiased for the entire range of magnitudes and colors that we have tested.
    The only noticeable feature is that the $(i-y)$ color at $i_{\mathrm{Input}}>24.0$ 
    is slightly overestimated.
    As mentioned above, this is not surprising given the shallower $y$ band 
    imaging depth. 
    Highly blended galaxies are less precise in their \forced{} \cmodel{} colors 
    compared to isolated galaxies.  
    Highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder  
    $(i-y)$ colors compared to their input colors.

>>>>

    Fig \ref{fig:cmodel_mag} shows the precision (\smag{}) and accuracy (\mmag{}) of 
    \cmodel{} magnitude in each band using the same format as Fig \ref{fig:psf_mag}.

@@

    The typical precision of $i$-band flux using \forced{} \cmodel{} is at 
    ${\sim}8-10$\% level in the \texttt{goodSeeing} \tract{} at 
    $i_{\mathrm{Input}}<24.0$ mag. 
    It moderately degrades to ${\sim}13$\% at $25.0$ mag. 
    The performance is similar in $i$ band for the \texttt{badSeeing} \tract{}. 
    At $20.0 < i_{\mathrm{Input}} < 24.0$ mag, the accuracies of \forced{} \cmodel{}
    magnitudes change between \plus{}$0.017$ mag to \minus{}$0.023$ mag. 
    At $24.0 < i_{\mathrm{Input}} < 25.5$ mag, \mmag{} is around $\minus0.006$ mag,
    which suggest that \forced{} \cmodel{} photometry is unbiased down to the very 
    faint end.

@@

    The precision of \forced{} \cmodel{} photometry is consistent across all filters.
    For the $g$, $r$, and $z$ bands, the statistical uncertainties are very similar to
    $i$-band results between $20.0$ and $25.0$ mag.
    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
    across the entire input magnitude range.
    The precision for the $y$ band is slightly worse, ranging from 10\% to 17\% in the
    same magnitude bins.
    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
    the $y$ band at $>24.0$ mag. 
    This bias in the $y$ band flux is equal to \minus{}0.07 at $24.0$ mag to 
    \minus{}0.22 mag at 25.0 mag. 
    Worse seeing conditions and a higher background noise level mean that it is more
    difficult to detect faint objects in the $y$ band.
    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
    around the detection threshold.

@@

    Fig \ref{fig:cmodel_color} evaluates the precision and accuracy of \forced{} 
    $(g-i)$ and $(i-y)$ \cmodel{} colors using the same format as 
    Fig \ref{fig:psf_color}. 
    We find that \hscpipe{} provides reliable \cmodel{} colors for synthetic 
    galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
    For $(g-i)$ colors, the statistical uncertainty at $i_{\mathrm{Input}}{\sim}20.0$ 
    mag is ${\sim}0.07$ mag.
    The statistical uncertainty increases to ${\sim}0.18$ mag at 
    $i_{\mathrm{Input}}{\sim}25.0$ mag.
    The $(i-y)$ colors show similar results, except the precision at 
    $i_{\mathrm{Input}}>24.0$ mag becomes slightly worse.

    The performance of \forced{} \cmodel{} color does not strongly depend on seeing 
    and is unbiased for the entire range of magnitudes and colors that we have tested.
    The only noticeable feature is that the $(i-y)$ color at $i_{\mathrm{Input}}>24.0$ 
    is systematically redder than the real values by $\plus0.05$ mag.
    As mentioned above, this is not surprising given the shallower $y$ band 
    imaging depth. 
    Highly blended galaxies are less precise in their \forced{} \cmodel{} colors 
    compared to isolated galaxies.  
    Highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder  
    $(i-y)$ colors compared to their input colors.
